### 2009-10-25 doc/manuals/user_interface/ui-conf.tex
Added Proxy and Configuration sections

\begin{framed}
\begin{verbatim}
[common]
attribute1=value1
attribute2=value2
attribute3=value3 value4
# comment line 1
# comment line 2
attribute2=value5
...
\end{verbatim}
\end{framed}

@@

The following blocks and respective attributes are recognized.

\section{Block \texttt{common}}

@@

where \texttt{service\_type} is type of service (e.g. \texttt{computing} or
\texttt{index}), \texttt{flavour} specifies type of middleware plugin to use
when contacting the service (e.g. ARC0, ARC1, CREAM, UNICORE, etc.) and
\texttt{service\_url} is the URL used to contact the service.

Example:
\begin{itemize}
\item{plain text:}\\ 
\verb#defaultservices=index:ARC0:ldap://index1.nordugrid.org:2135/Mds-Vo-name=NorduGrid,o=grid index:ARC1:https://knowarc2.grid.niif.hu:50000/isis computing:ARC1:https://knowar c1.grid.niif.hu:60000/arex computing:CREAM:ldap://cream.grid.upjs.sk:2170/o=grid computing:UNICORE:https://testbed5.grid.upjs.sk:8080/KnowARC-testbed/services/BESFactory?res=default_bes_factory#
\end{itemize}

% \phantomsection
% \index{configuration:giis}\addcontentsline{toc}{subsection}{giis}
% \hspace*{0.5cm}
% \begin{shaded}
%   \uicommand{giis}
% \end{shaded}
% \textbf{This attribute is multi-valued.}
% 
% Configures which GIISes (site indices) to use to discover computing
% and storage resources. The default is to use the four top level
% GIISes:
% 
% \begin{verbatim}
%   ldap://index1.nordugrid.org:2135/O=Grid/Mds-Vo-name=NorduGrid
%   ldap://index2.nordugrid.org:2135/O=Grid/Mds-Vo-name=NorduGrid
%   ldap://index3.nordugrid.org:2135/O=Grid/Mds-Vo-name=NorduGrid
%   ldap://index4.nordugrid.org:2135/O=Grid/Mds-Vo-name=NorduGrid
% \end{verbatim}
% 
% Examples:
% \begin{itemize}
% \item{plain text:}\\ 
% \verb#    giis="ldap://atlasgiis.nbi.dk:2135/O=Grid/Mds-Vo-name=Atlas"#\\
% \verb#    giis="ldap://index1.nordugrid.org:2135/O=Grid/Mds-Vo-name=NorduGrid"#\\
% \verb#    giis="ldap://grid.tsl.uu.se:2135/O=Grid/Mds-Vo-name=local"#
% \item{XML:}\\ 
% \verb#    <giis>ldap://odin.switch.ch:2135/O=Grid/Mds-Vo-name=Switzerland</giis>#\\
% \verb#    <giis>ldap://index1.nordugrid.org:2135/O=Grid/Mds-Vo-name=NorduGrid</giis>#\\
% \verb#    <giis>ldap://grid.tsl.uu.se:2135/O=Grid/Mds-Vo-name=local</giis>#
% \end{itemize}
% 
% \begin{framed}
% Note that LDAP URLs containing "Mds-Vo-name=local" refer not to
% GIISes, but to individual sites. This feature can be used to add
% "hidden" sites that do not register to any GIIS, or to list explicitly
% preferred submission sites.
% \end{framed}
% 
% \phantomsection
% \index{configuration:debug}\addcontentsline{toc}{subsection}{debug}
% \hspace*{0.5cm}
% \begin{shaded}
%   \uicommand{debug}
% \end{shaded}
% Default debug level to use for the ARC clients. Corresponds to the \verb#-d#
% command line switch of the clients. Default value is 0, possible range
% is from -3 to 3.
% 
% Examples:
% \begin{itemize}
% \item{plain text:}\\ \verb#    debug="2"#
% \item{XML:}\\ \verb#    <debug>2</debug>#
% \end{itemize}
% 
% 
% \phantomsection
% \index{configuration:timeout}\addcontentsline{toc}{subsection}{timeout}
% \hspace*{0.5cm}
% \begin{shaded}
%   \uicommand{timeout}
% \end{shaded}
% Timeout to use for interaction with LDAP servers, gridftp servers,
% etc. If a server, during e.g. job submission, does not answer in the
% specified number of seconds, the connection is timed out and
% closed. Default value is 20 seconds.
% 
% Examples:
% \begin{itemize}
% \item{plain text:}\\ \verb#    timeout="20"#
% \item{XML:}\\ \verb#    <timeout>10</timeout>#
% \end{itemize}
% 
% 
% \phantomsection
%
\index{configuration:downloaddir}\addcontentsline{toc}{subsection}{downloaddir}
% \hspace*{0.5cm}
% \begin{shaded}
%   \uicommand{downloaddir}
% \end{shaded}
% Default download directory to download files to when retrieving output
% files from jobs using \texttt{ngget}.  Default is the current working
% directory.
% 
% Examples:
% \begin{itemize}
% \item{plain text:}\\ \verb#    downloaddir="/home/johndoe/arc-downloads"#
% \item{XML:}\\ \verb#    <downloaddir>/tmp/johndoe</downloaddir>#
% \end{itemize}
% 
% 
% \phantomsection
% \index{configuration:alias}\addcontentsline{toc}{subsection}{alias}
% \hspace*{0.5cm}
% \begin{shaded}
%   \uicommand{alias}
% \end{shaded}
% \textbf{This attribute is multi-valued.}
% 
% Alias substitutions to perform in connection with the \verb#-c# command line
% switch of the ARC clients. Alias definitions are recursive. Any alias
% defined in a block that is read before a given block can be used in
% alias definitions in that block. An alias defined in a block can also
% be used in alias definitions later in the same block.
% 
% Examples:
% \begin{itemize}
% \item{plain text:}\\ \verb#    alias="host1=somehost.nbi.dk"#\\
% \verb#    alias="host2=otherhost.uu.se"#\\
% \verb#    alias="myhosts=host1 host2"#
% \item{XML:}\\ \verb#    <alias>host1=somehost.nbi.dk</alias>#\\
% \verb#    <alias>host2=otherhost.uu.se</alias>#\\
% \verb#    <alias>myhosts=host1 host2</alias>#
% \end{itemize}
% 
% With the example above, \verb#ngsub -c myhosts# will resolve to \verb#ngsub -c somehost.nbi.dk -c otherhost.uu.se#.
% 
% \phantomsection
% \index{configuration:broker}\addcontentsline{toc}{subsection}{broker}
% \hspace*{0.5cm}
% \begin{shaded}
%   \uicommand{broker}
% \end{shaded}
% Configures which brokering algorithm to use during job submission. The
% default one is the \texttt{FastestCpus} broker that chooses, among the
% possible targets, the target with the fastest CPUs. Another
% possibility is, for example, the
% \texttt{RandomSort} broker that chooses the target randomly among the targets
% surviving the job description matchmaking.
% 
% Examples:
% \begin{itemize}
% \item{plain text:}\\ \verb#    broker="RandomSort"#
% \item{XML:}\\ \verb#    <broker>RandomSort</broker>#
% \end{itemize}

@@

ARC configuration file in releases 0.6 and 0.8 has the same name and the same
format; attributes unknown to newer ARC versions are ignored.

>>>>

\begin{framed}
\begin{verbatim}
[common]
attribute1=value1
attribute2=value2
attribute3=value3 value4
# comment line 1
# comment line 2
...
\end{verbatim}
\end{framed}

@@

Most attributes have counterpart command line options. Command line options
always overwrite configuration attributes.

Two blocks are currently recognized, \texttt{[common]} and
\texttt{[alias]}. Following sections describe supported attributes per block.

\section{Block \texttt{[common]}}

@@

where \texttt{service\_type} is type of service (e.g. \texttt{computing} or
\texttt{index}), \texttt{flavour} specifies type of middleware plugin to use
when contacting the service (e.g. ARC0, ARC1, CREAM, UNICORE, etc.) and
\texttt{service\_url} is the URL used to contact the service. Several services
can be listed, separated with a blank space (no line breaks allowed).

Example:
\begin{verbatim*} 
defaultservices=index:ARC0:ldap://index1.ng.org:2135/Mds-Vo-name=testvo,o=grid
 index:ARC1:https://index2.ng.org:50000/isis
 computing:ARC1:https://ce.arc.org:60000/arex
 computing:CREAM:ldap://ce.glite.org:2170/o=grid
 computing:UNICORE:https://ce.unicore.org:8080/test/services/BESFactory?res=default_bes_factory
\end{verbatim*}

\phantomsection
\index{configuration:rejectservices}\addcontentsline{toc}{subsection}{rejectservices}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{rejectservices}
\end{shaded}
\textbf{This attribute is multi-valued.}

This attribute can be used to indicate that a certain service should be
rejected (``blacklisted''). Several services can be listed, separated with a
blank space (no line breaks allowed).

Example:
\verb#    rejectservices=computing:ARC1:https://bad.service.org/arex#

 \phantomsection
 \index{configuration:verbosity}\addcontentsline{toc}{subsection}{verbosity}
 \hspace*{0.5cm}
 \begin{shaded}
   \uicommand{verbosity}
 \end{shaded}
 Default verbosity (debug) level to use for the ARC clients. Corresponds to the
\verb#-d# command line option of the clients. Default value is \texttt{WARNING},
possible values are \texttt{FATAL}, \texttt{ERROR}, \texttt{WARNING},
\texttt{INFO}, \texttt{DEBUG} or \texttt{VERBOSE}.

Example:
\verb#    verbosity=INFO#

\phantomsection
\index{configuration:timeout}\addcontentsline{toc}{subsection}{timeout}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{timeout}
\end{shaded}
Sets the period of time the client should wait for a service (information,
computing, storage etc) to respond when communicating with it. The period
should be given in seconds. Default value is 20 seconds. This attribute
corresponds to the \verb#-t# command line option.

Example:
\verb#    timeout=10#

\phantomsection
\index{configuration:brokername}\addcontentsline{toc}{subsection}{brokername}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{brokername}
\end{shaded}

Configures which brokering algorithm to use during job submission. This attribute
corresponds to the \verb#-b# command line option. The
default one is the \texttt{Random} broker that chooses targets randomly.
Another possibility is, for example, the \texttt{FastestQueue} broker that
chooses the target with the shortest estimated queue waiting time. Possible
values are:
\begin{itemize}
 \item[\texttt{Random}] -- ranks targets randomly (default)
 \item[\texttt{FastestQueue}] -- ranks targets according to their queue length
% \item[\texttt{FastestCPU}] -- ranks targets according to CPU performance
 \item[\texttt{Data}] -- ranks target according the amount of megabytes of the
requested input files that are already in the computing resource’s cache.
% \item[\texttt{SampleBroker}] -- Ranks targets randomly (written in Python)
\end{itemize}

 Example:
\verb#    brokername=Data#

\phantomsection
\index{configuration:brokerarguments}\addcontentsline{toc}{subsection}{brokerarguments}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{brokerarguments}
\end{shaded}

This attribute is used in case a broker comes with arguments.

Example:
\verb#    brokerarguments=cow#

\phantomsection
\index{configuration:joblist}\addcontentsline{toc}{subsection}{joblist}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{joblist}
\end{shaded}

Path to the job list file. This file will be used by commands such as \texttt{arcsub}, \texttt{arcstat},
\texttt{arcsync} etc. to read and write information about jobs. This attribute
corresponds to the \verb#-j# command line option. The default
location of the file is in the {\$}HOME/.arc/client.conf directory with the
name \texttt{jobs.xml}.

Example:
\begin{verbatim}
    joblist=/home/user/run/jobs.xml
    joblist=C:\\run\jobs.xml
\end{verbatim}

\phantomsection
\index{configuration:bartender}\addcontentsline{toc}{subsection}{bartender}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{bartender}
\end{shaded}

Specifies default \textit{Bartender} services. Multiple Bartender URLs should
be separated with a blank space.
These URLs are used by the \texttt{chelonia} command line tool, the Chelonia
FUSE plugin and by the data tool commands \texttt{arccp}, \texttt{arcls}, \texttt{arcrm}, etc..

Example:
\verb#    bartender=http://my.bar.com/tender#

\phantomsection
\index{configuration:proxypath}\addcontentsline{toc}{subsection}{proxypath}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{proxypath}
\end{shaded}

Specifies a non-standard location of proxy certificate. It is used by
\texttt{arcproxy} or similar tools during proxy generation, and all other tools
during establishing of a secure connection. This attribute
corresponds to the \verb#-P# command line option of \texttt{arcproxy}.

Example:
\verb#    proxypath=/tmp/my-proxy#

\phantomsection
\index{configuration:keypath}\addcontentsline{toc}{subsection}{keypath}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{keypath}
\end{shaded}

Specifies a non-standard location of user's private key. It is used by
\texttt{arcproxy} or similar tools during proxy generation. This attribute
corresponds to the \verb#-K# command line option of \texttt{arcproxy}.

Example:
\verb#    keypath=/home/username/key.pem#

\phantomsection
\index{configuration:certificatepath}\addcontentsline{toc}{subsection}{certificatepath}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{certificatepath}
\end{shaded}

Specifies a non-standard location of user's public certificate. It is used by
\texttt{arcproxy} or similar tools during proxy generation. This attribute
corresponds to the \verb#-C# command line option of \texttt{arcproxy}.

Example:
\verb#    certificatepath=/home/username/cert.pem#

\phantomsection
\index{configuration:cacertificatesdirectory}\addcontentsline{toc}{subsection}{cacertificatesdirectory}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{cacertificatesdirectory}
\end{shaded}

Specifies non-standard location of the directory containing CA-certificates.
This attribute
corresponds to the \verb#-T# command line option of \texttt{arcproxy}.

Example:
\verb#    cacertificatesdirectory=/home/user/cacertificates#

\phantomsection
\index{configuration:cacertificatepath}\addcontentsline{toc}{subsection}{cacertificatepath}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{cacertificatepath}
\end{shaded}

Specifies an explicit path to the certificate of the CA that issued user's credentials.

Example:
\verb#    cacertificatepath=/home/user/myCA.0#

\phantomsection
\index{configuration:vomsserverpath}\addcontentsline{toc}{subsection}{vomsserverpath}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{vomsserverpath}
\end{shaded}

Specifies non-standard path to the file which contians list of VOMS services and
associated configuration parameters. This attribute
corresponds to the \verb#-V# command line option of \texttt{arcproxy}.

Example:
\verb#    vomsserverpath=/etc/voms/vomses#

\phantomsection
\index{configuration:username}\addcontentsline{toc}{subsection}{username}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{username}
\end{shaded}

Sets default username to be used for requesting credentials from Short Lived
Credentials Service. This attribute
corresponds to the \verb#-U# command line option of \texttt{arcslcs}.

Example:
\verb#    username=johndoe#

\phantomsection
\index{configuration:password}\addcontentsline{toc}{subsection}{password}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{password}
\end{shaded}

Sets default password to be used for requesting credentials from Short Lived
Credentials Service. This attribute
corresponds to the \verb#-P# command line option of \texttt{arcslcs}.

Example:
\verb#    password=secret#

\phantomsection
\index{configuration:keypassword}\addcontentsline{toc}{subsection}{keypassword}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{keypassword}
\end{shaded}

Sets default password to be used to encode the private key of credentials obtained
from a Short Lived Credentials Service. This attribute
corresponds to the \verb#-K# command line option of \texttt{arcslcs}.

Example:
\verb#    keypassword=secret2#

\phantomsection
\index{configuration:keysize}\addcontentsline{toc}{subsection}{keysize}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{keysize}
\end{shaded}

Sets size (strength) of the private key of credentials obtained from a Short
Lived Credentials Service. Default value is 1024. This attribute
corresponds to the \verb#-Z# command line option of \texttt{arcslcs}.

Example:
\verb#    keysize=2048#

\phantomsection
\index{configuration:certificatelifetime}\addcontentsline{toc}{subsection}{certificatelifetime}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{certificatelifetime}
\end{shaded}

Sets lifetime (in hours, starting from current time) of user certificate which
will be obtained from a Short Lived Credentials Service. This attribute
corresponds to the \verb#-L# command line option of \texttt{arcslcs}.

Example:
\verb#    certificatelifetime=12#

\phantomsection
\index{configuration:slcs}\addcontentsline{toc}{subsection}{slcs}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{slcs}
\end{shaded}

Sets the URL to the Short Lived Certificate Service. This attribute
corresponds to the \verb#-S# command line option of \texttt{arcslcs}.

Example:
\verb#    slcs=https://127.0.0.1:60000/slcs#

\phantomsection
\index{configuration:storedirectory}\addcontentsline{toc}{subsection}{storedirectory}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{storedirectory}
\end{shaded}

Sets directory which will be used to store credentials obtained from a Short
Lived Credential Servise. This attribute
corresponds to the \verb#-D# command line option of \texttt{arcslcs}.

Example:
\verb#    storedirectory=/home/mycredentials#

\phantomsection
\index{configuration:idpname}\addcontentsline{toc}{subsection}{idpname}
\hspace*{0.5cm}
\begin{shaded}
  \uicommand{idpname}
\end{shaded}

Sets Identity Provider name (Shibboleth) to which user belongs. It is used for
contacting Short Lived Certificate Services. This attribute
corresponds to the \verb#-I# command line option of \texttt{arcslcs}.

Example:
\verb#    idpname=https://idp.testshib.org/idp/shibboleth#

\section{Block \texttt{[alias]}}

Users often prefer to submit jobs to a specific site; since contact URLs (and
especially end-point references) are very long, it is very convenient to replace
them with aliases. Block \texttt{[alias]} simply contains a list of
alias-value pairs.

 Alias substitutions is performed in connection with the \verb#-c# command line
 switch of the ARC clients.

 Aliases can refer to a list of services (separated by a blank space).

 Alias definitions can be recursive. Any alias
 defined in a list that is read before a given list can be used in
 alias definitions in that list. An alias defined in a list can also
 be used in alias definitions later in the same list.

 Examples:
\begin{verbatim}
[alias]

arc0=computing:ARC0:ldap://ce.ng.org:2135/nordugrid-cluster-name=ce.ng.org,Mds-Vo-name=local,o=grid
arc1=computing:ARC1:https://arex.ng.org:60000/arex
cream=computing:CREAM:ldap://cream.glite.org:2170/o=grid
unicore=computing:UNICORE:https://bes.unicore.org:8080/test/services/BESFactory?res=default_bes
crossbrokering=arc0 arc1 cream unicore
\end{verbatim}

@@

ARC configuration file in releases 0.6 and 0.8 has the same name and the same
format. Only one attribute is preserved (\texttt{timeout}); other attributes
unknown to newer ARC versions are ignored.

### 2009-10-25 doc/manuals/user_interface/ui-job.tex
Added Proxy and Configuration sections

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcsub [options]}%$<$task ...$>$
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{ -c, --cluster}&\verb#[-]#\textit{url}&explicitly select or reject a specific site (cluster)\\
   \texttt{ -i, --indexurl}&\textit{url}&URL of an index server\\
   \texttt{ -e, --jobdescrstring}&\textit{filename}&string describing the job to be submitted\\
   \texttt{ -f, --jobdescrfile}&\textit{filename}&file describing the job to be submitted\\
   \texttt{ -j, --joblist}&\textit{filename}&file where the job IDs will be stored\\
   \texttt{ -D, --dryrun}&&add dryrun option to the job description\\
   \texttt{ -x, --dumpdescription}&&do not submit -- dump transformed job description to stdout\\
   \texttt{ -t, --timeout}&\textit{time}&timeout for queries in seconds (default 20)\\
   \texttt{ -d, --debug}&\textit{debuglevel}&debug level, FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE - default WARNING\\
   \texttt{ -U, --unknownattr}&&allow unknown attributes in the job description\\
   \texttt{ -v, --version}&&print version information\\
   \texttt{ -?, --help}&&print help page\\
%   Arguments:&&\\
%   \texttt{ task ...}&&strings or files describing the jobs to be submitted\\
\end{longtable}

@@

\begin{shaded}
   \uicommand{arcstat [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-i, --joblist}& \textit{filename}& file containing a list of jobIDs\\
   \texttt{-c, --cluster}& & show information about a site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-i, --indexurl}& \textit{url} &URL of an index service\\
   \texttt{-q, --queues}&&show information about clusters and queues\\
   \texttt{-l, --long}& & long format (extended information)\\
   \texttt{-t, --timeout}& \textit{time}& timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arccat [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-i, --joblist}& \textit{filename} & file containing a list of job IDs\\
   \texttt{-c, --cluster}& & show information about clusters\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-o, --stdout}& & show the stdout of the job (default)\\
   \texttt{-e, --stderr}& & show the stderr of the job\\
   \texttt{-l, --gmlog}& & show the grid manager's error log of the job\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcget [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-i, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-D, --dir} & \textit{dirname} & download directory (the job directory will be created in this directory)\\
   \texttt{-k, --keep}& & keep files on gatekeeper (do not clean)\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arckill [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}& & show information about clusters\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-k, --keep}& & keep files on gatekeeper (do not clean)\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcclean [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-f, --force} & & removes the job ID from the local list\\
   & &~~~even if the job is not found on the Grid\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

>>>>

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcsub [options]}%$<$task ...$>$
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-c, --cluster}&\verb#[-]#\textit{url}&explicitly select or reject a specific site (cluster)\\
   \texttt{-i, --indexurl}&\textit{url}&URL of an index server\\
   \texttt{-e, --jobdescrstring}&\textit{filename}&string describing the job to be submitted\\
   \texttt{-f, --jobdescrfile}&\textit{filename}&file describing the job to be submitted\\
   \texttt{-j, --joblist}&\textit{filename}&file where the job IDs will be stored\\
   \texttt{-D, --dryrun}&&add dryrun option to the job description\\
   \texttt{-x, --dumpdescription}&&do not submit -- dump transformed job description to stdout\\
   \texttt{-U, --unknownattr}&&allow unknown attributes in the job description\\
   \texttt{-t, --timeout}&\textit{time}&timeout for queries in seconds (default 20)\\
   \texttt{-d, --debug}&\textit{debuglevel}&debug level, FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE - default WARNING\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-v, --version}&&print version information\\
   \texttt{-h, --help}&&print help page\\
%   Arguments:&&\\
%   \texttt{ task ...}&&strings or files describing the jobs to be submitted\\
\end{longtable}

@@

\begin{shaded}
   \uicommand{arcstat [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-i, --joblist}& \textit{filename}& file containing a list of jobIDs\\
   \texttt{-c, --cluster}& & show information about a site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-i, --indexurl}& \textit{url} &URL of an index service\\
   \texttt{-q, --queues}&&show information about clusters and queues\\
   \texttt{-l, --long}& & long format (extended information)\\
   \texttt{-t, --timeout}& \textit{time}& timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arccat [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-i, --joblist}& \textit{filename} & file containing a list of job IDs\\
   \texttt{-c, --cluster}& & show information about clusters\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-o, --stdout}& & show the stdout of the job (default)\\
   \texttt{-e, --stderr}& & show the stderr of the job\\
   \texttt{-l, --gmlog}& & show the grid manager's error log of the job\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcget [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-i, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-D, --dir} & \textit{dirname} & download directory (the job directory will be created in this directory)\\
   \texttt{-k, --keep}& & keep files on gatekeeper (do not clean)\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arckill [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}& & show information about clusters\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-k, --keep}& & keep files on gatekeeper (do not clean)\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcclean [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-f, --force} & & removes the job ID from the local list even if the job is not found on the Grid\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}
